Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 overall.tex
Address Jack's issue #13

It should be noted that increasing the number of brokers requires also to
increase the number of concurrent jobs that can be submitted to Titan's queue.
Each broker submits 1 job at a time with at least 2 hours walltime. Backfill
availability is polled every 10 minutes, giving a theoretical maximum of 110
concurrent jobs submitted to Titan. Titan's policy was already changed in
September 2016, enabling the submission of 20 concurrent jobs and the deployment
of 20 PanDA brokers. Further study is required to understand the impact that a
larger amount of concurrent queued jobs would have on the overall efficiency of
Titan's scheduler.

>>>>

It should be noted that increasing the number of brokers requires also to
increase the number of concurrent jobs that can be submitted to Titan's queue.
Each broker submits 1 job at a time, asking for no more than 300 worker nodes
and at least 2 hours walltime. When backfill availability exceeds 300 worker
nodes, multiple brokers are used to submit multiple jobs. Backfill availability
is polled every 10 minutes, giving a maximum of 11 concurrent sets of jobs
submitted to Titan. Considering the variable amount of time spent by each job in
Titan's queue, a large number of brokers and concurrent queued jobs may be
required to use all the backfill availability.

Titan's policy was already changed in September 2016, enabling the submission of
20 concurrent jobs. As shown in Fig.~\ref{fig:backfill-utilization}, this
improved the efficiency of PanDA brokers but further study is required to
understand the impact that a larger amount of concurrent queued jobs would have
on the overall efficiency of Titan's scheduler.
